Out-of-Sample Comparisons of Overfit Models

### 2017-05-05 D1-example.tex
[#40/move] Change graphics reflecting in-sample rejection

\input{floats/circles}
\begin{figure}[t!]
  \centering
  \begin{tabular}{cc}
  \subfloat[]{\circlefigA{1}{2.5}{1.4}{4.5}\label{fig:circleA}} &
  \subfloat[]{\circlefigB{1}{2.5}{1.4}{4.5}\label{fig:circleB}}
  \end{tabular}
  \caption{Graphs indicating the rejection region and region of equal
    generalization error for the models discussed in Section
    \ref{sec:insample}.  The smaller model has no estimated parameters
    and the larger has two coefficients.  The shaded regions in
    Figures (a) and (b) show the rejection region and the acceptance
    region respectively of the full-sample test given $\E_T \oosB \leq
    0$. Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
    selection vectors, so the horizontal axes represent changes in the
    first unique element of $\bh{2T}$ and the vertical axes represent
    changes in the second unique element.}
\label{fig:rreject}
\end{figure}

>>>>

\input{floats/circles}
\begin{figure}[t!]
  \centering
  \begin{tabular}{cc}
  \subfloat[]{\circlefigA{1}{2.5}{1.4}{4.5}\label{fig:circleA}} &
  \subfloat[]{\circlefigB{1}{2.5}{1.4}{4.5}\label{fig:circleB}}
  \end{tabular}
  \caption{Graphs indicating the rejection region and region of equal
    generalization error for the models discussed in Section
    \ref{sec:insample}.
    In Figure (a), the union of
    the two shaded areas shows the parameter estimates consistent
    with the null hypothesis $\E_T \oosB \leq 0$ and in Figure (b), the union of
    the two shaded areas shows the parameter estimates consistent
    with the alternative hypothesis $\E_T \oosB > 0$. The
    dark gray circles are contour lines for the sampling density of
    $M_2 \bh{2T}$, at increments of 0.01. In both figures, the lighter
    region shows the rejection region of the F-test and the darker
    region shows its acceptance region.
    Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
    selection vectors, so the horizontal axes represent changes in the
    first unique element of $\bh{2T}$ and the vertical axes represent
    changes in the second unique element.}
\label{fig:rreject}
\end{figure}
